### 2023-06-06 main.tex
Exchange-Double-Row

\cite{Sklyanin:1988yz}
\subsection{Quantum inverse scattering method}
We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
\begin{equation}\label{Rmatrix}
R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
\end{equation}
\begin{equation}\label{KmatrixHAT}
\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
\end{equation}
\begin{equation}\label{Kmatrix}
K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
\end{equation}
The above matrices satisfy the following equations
\begin{itemize}
\item \textit{Yang-Baxter-Equation}
\begin{equation}
R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
\end{equation}
\item \textit{Boundary-Yang-Baxter-Equation}
\begin{equation}
R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
\end{equation}
\item \textit{Dual Boundary-Yang-Baxter-Equation}
\begin{equation}
K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
\end{equation}
\end{itemize}
We define the following \textit{transfer matrix}
\begin{equation}
	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
\end{equation}
where we used the double row monodromy
\begin{equation}
	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
\end{equation}
where 
\begin{equation}
	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
\end{equation}
This trasfer matrix has the following properties
\begin{equation}
	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
\end{equation}
with $C_{1},C_{2}>0$. \\
We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
\begin{equation}
	U_{0}(x)=\begin{pmatrix}
		A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
		C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
		\vdots&\vdots&\ddots&\vdots\\
		C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
	\end{pmatrix}
\end{equation}
In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain
\begin{equation}
	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
		1+x&0&\ldots&0\\
		0&1-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		0&0&\ldots&1-x
	\end{pmatrix}
\end{equation}
\begin{equation}
	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
		N+x&0&\ldots&0\\
		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
	\end{pmatrix}
\end{equation}
Then we obtain the correspondent transfer matrix as
\begin{equation}
	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
\end{equation}
where
\begin{equation}
	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
\end{equation}
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
\begin{equation}
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}

>>>>

\cite{Sklyanin:1988yz}
\subsection{Quantum inverse scattering method}
We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
\begin{equation}\label{Rmatrix}
R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
\begin{equation}\label{KmatrixHAT}
\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
\begin{equation}\label{Kmatrix}
K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
The above matrices satisfy the following equations
\begin{itemize}
\item \textit{Yang-Baxter-Equation}
R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
\item \textit{Boundary-Yang-Baxter-Equation}
R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
\item \textit{Dual Boundary-Yang-Baxter-Equation}
K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
\end{itemize}
We define the following \textit{transfer matrix}
	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
where we used the double row monodromy
	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
This double row monodromy satisfies the following exchange relation
	R_{ab}(x-y)U_{a}(x)R_{ab}(x+y)U_{b}(y)=U_{b}(y)R_{ab}(x+y)U_{a}(x)R_{ab}(x-y)
This trasfer matrix has the following properties
	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
with $C_{1},C_{2}>0$. \\
We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
	U_{0}(x)=\begin{pmatrix}
In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain
	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
		1+x&0&\ldots&0\\
		0&1-x&\ldots&0\\
		0&0&\ldots&1-x
	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
Then we obtain the correspondent transfer matrix as
	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
